Blas\'e3D

### 2023-10-10 paper/paper2/ms.tex
Tiny comment
Paper work
Pair coding on the outline, fun!

\usepackage{amsmath}
\usepackage{blindtext}

\usepackage{mdframed}

@@

\section{Data}
\begin{mdframed}
    \textbf{PHOENIX Model Grid Subset}

@@

\begin{mdframed}
    \textbf{Figure: Line Population Heatmap}
\end{mdframed}

\section{Methods}
\begin{mdframed}
    \textbf{Illustration}
\end{mdframed}

\begin{mdframed}
    \textbf{Model Optimization}

    - Per-grid point optimization procedure
    - Optimization outputs
    - Output storage

@@

\begin{mdframed}
    \textbf{Line Recognition}

    - Line set
    - Pre-shift centers

@@

\begin{mdframed}
    \textbf{Math of the Surface Fit}

>>>>

\usepackage{amsmath}
\usepackage{blindtext}
% Temporary packages
\usepackage{mdframed}

@@

\section{Emulating the PHOENIX grid}

\begin{mdframed}
    \textbf{The PHOENIX grid subset}

@@

\begin{mdframed}
    \textbf{Emulation with blas\'e}

    - Per-grid point optimization procedure
    - Pretrained model caching
    - Output storage

@@

\begin{mdframed}
    \textbf{Open Source Availability}

@@

\begin{mdframed}
    \textbf{Figure: Line density across the grid heatmap}
\end{mdframed}

\section{Line-by-Line Fundamental Stellar Properties}
\begin{mdframed}
    \textbf{Conceptual Illustration: Faceted Plot (Teff, Logg, Z) -> Line Profiles}
\end{mdframed}

\begin{mdframed}
    \textbf{Line Recognition}
    - Need: Identifying unique lines
    - Anticipated friction points: line centroids drift
    - Strategy: (Pre-shift centers)
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

\begin{mdframed}
    \textbf{Line property trends across the grid}
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

\begin{mdframed}
    \textbf{Figure: Heatmap $T_\mathrm{eff}$ vs $\log{g}$ for a single line $2\times2$ panels for $\sigma$, $\gamma$, $A$, $\lambda$ }
\end{mdframed}

\begin{mdframed}
    \textbf{Line-by-Line Parameter Surfaces}
